\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

% PACKAGES
\usepackage{amsmath} % For extended formatting
\usepackage{amssymb} % For math symbols
\usepackage{amsthm} % For proof environment
\usepackage{array} % For tables
\usepackage{enumerate} % For lists
\usepackage{extramarks} % For headers and fo
% DOCUMENT FORMATING
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

% PACKAGES
\usepackage{amsmath} % For extended formatting
\usepackage{amssymb} % For math symbols
\usepackage{amsthm} % For proof environment
\usepackage{array} % For tables
\usepackage{enumerate} % For lists
\usepackage{extramarks} % For headers and footers
\usepackage{fancyhdr} % For custom headers
\usepackage{graphicx} % For inserting images
\usepackage{multicol} % For multiple columns
\usepackage{verbatim} % For displaying code
\usepackage{tkz-euclide}
\usepackage{pgfplots}

% SET UP HEADER AND FOOTER
\pagestyle{fancy}
\lhead{\MyCourse} % Top left header
\chead{\MyTopicTitle} % Top center header
\rhead{\MyAssignment} % Top right header
\lfoot{\MyCampus} % Bottom left footer
\cfoot{} % Bottom center footer
\rfoot{\MySemester} % Bottom right footer
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand\footrulewidth{0.4pt} % Size of the footer rule

\newcommand{\MyCourse}{Math 241}
\newcommand{\MyTopicTitle}{Derivatives}
\newcommand{\MyAssignment}{Name: \qquad \qquad \qquad}
\newcommand{\MySemester}{FALL 2019}
\newcommand{\MyCampus}{University of Hawaii at Manoa}
\begin{document}

\section{Definition of a Derivative}
\begin{equation}
    \lim_{h\to0}\frac{f(x+h)-f(x)}{h}
\end{equation}
Derivative tells us the change of the function. \newline 
For instance if f(x) tells us the position of an object, then its derivative (written as $f'(x) or \frac{d}{dx}f(x)$) tells us the speed. 
\section{Derivative Properties}
Sometimes memorizing these derivatives properties will help you in the later calculus. 
\begin{center}
    \textbf{Caution}
\end{center}
Carefully read the direction of the problem as it may ask you to solve using 
the definition of a derivatives. Even with the correct answer it may hurt your score.   
\subsection{Constant Rule}
\begin{equation}
    \frac{d}{dx}c = 0
\end{equation} where c is any real number \newline
A derivative of any constant is equal to 0.
\subsection{derivative of a single variable}
\begin{equation}
    \frac{d}{dx}x = 1
\end{equation}
where x is a variable to the first power
\subsection{Power Rule}
\begin{equation}
    \frac{d}{dx}x^{n} = nx^{n-1}
\end{equation}
where n is a real number 
\subsection{Product Rule}
\begin{equation}
    \frac{d}{dx}(f(x)\times g(x)) = (\frac{d}{dx}f(x))g(x) + f(x)(\frac{d}{dx}g(x))
\end{equation}
\subsection{Quotient Rule}
\begin{equation}
        \frac{d}{dx}((f(x) \div g(x))=\frac{(\frac{d}{dx}f(x))g(x) - f(x)\frac{d}{dx}g(x)}{(g(x)^{2})}
\end{equation}



\section{Trigonometry Derivatives}
\begin{itemize}
    \item $\frac{d}{dx}sin(x) = cos(x)$
    \newline 
    \item$\frac{d}{dx}cos(x) = -sin(x) $
    \newline 
    \item $\frac{d}{dx}tan(x) = sec^{2}(x)$ 
    \newline 
    \item $\frac{d}{dx} sec(x) = sec(x)tan(x)$
    \newline
    \item $\frac{d}{dx} csc(x) = -csc(x)cot(x)$
    \newline 
    \item $\frac{d}{dx} cot(x) = -csc^{2}(x)$
    \newline 
    \item \textbf{advice} trigonometry functions that start with the letter 'C' have a negative sign on its their derivative. 
\end{itemize}
\section{Application of Derivatives}
\begin{itemize}
    \item \textbf{Critical Points}: x=c is a critical point of a function if $ f'(c)=0 $ or $f'(c)=$ DNE
    \item \textbf{Maximum & Minimum}: since the derivatives tells us if the slope of the graph is increasing or decreasing we can find the use it to find the highest or/and lowest points
    \item \textbf{Tangent Lines}
    \begin{equation}
        y= f(a) + f'(a)(x-a)  
    \end{equation}based on the points (a, f(a))
\end{itemize}
\end{document}oters
\usepackage{fancyhdr} % For custom headers
\usepackage{graphicx} % For inserting images
\usepackage{multicol} % For multiple columns
\usepackage{verbatim} % For displaying code
\usepackage{tkz-euclide}
\usepackage{pgfplots}

% SET UP HEADER AND FOOTER
\pagestyle{fancy}
\lhead{\MyCourse} % Top left header
\chead{\MyTopicTitle} % Top center header
\rhead{\MyAssignment} % Top right header
\lfoot{\MyCampus} % Bottom left footer
\cfoot{} % Bottom center footer
\rfoot{\MySemester} % Bottom right footer
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand\footrulewidth{0.4pt} % Size of the footer rule
\newcommand{\MyCourse}{Math 241}
\newcommand{\MyTopicTitle}{Integrals}
\newcommand{\MyAssignment}{Name: \qquad \qquad \qquad}
\newcommand{\MySemester}{FALL 2019}
\newcommand{\MyCampus}{University of Hawaii at Manoa}
\begin{document}
\section{Definition of Integral}
An integral of a function is the anti-derivative of it. 
\begin{equation}
    \int f(x) dx = F(x) + C
\end{equation}
\textbf{Caution} If the integral is indefinite \textbf{(No specific bounds)} then write down the letter C. 
\subsection{Properties of the Integral}
\begin{equation}
    \int k f(x) dx = k \int f(x) dx
\end{equation}
where k is any constant.
\begin{equation}
    \int -f(x) dx = - \int f(x) dx 
\end{equation}
\begin{equation}
    \int f(x) \pm g(x) dx= \int f(x) dx \pm \int g(x) dx  
\end{equation}
\begin{equation}
    \int a dx = ax + C
\end{equation} where a is a constant 

\begin{equation}
    \int x^{n} = \frac{x^{n+1}}{n+1}
\end{equation}
\subsection{Properties of Definite Integrals}
\textbf{Definite Integrals} means an integral with a certain bounds. 
Written as $\int_{a}^{b} f(x) dx$ where f(x) represents a certain function and b and a represents the boundary areas. \newline 
\begin{equation}
    \int_{a}^{b} f(x) dx = - \int_{b}^{a} f(x) dx 
\end{equation}
\begin{equation}
      \int_{a}^{a} f(x) dx = 0
\end{equation}
\begin{equation}
    \int_{a}^{b}f(x)dx \pm \int_{b}^{c}f(x)dx = \int_{a}^{c} f(x)dx
\end{equation}
where a, b, and c represents a boundary point. 
\section{Integration by Substitution}

\section{Trigonometry Integrals}
\begin{itemize}
    \item $\int sin(x) dx = -cos(x)+C$
    \item $\int cos(x) dx = sin(x)+C$
    \item $\int sec^{2}(x)dx = tan(x)+C$
    \item $\int csc^{2}(x)dx = cot(x)+C$
    \item $\int sec(x)tan(x) dx = sec(x)+C$
    \item $\int csc(x)cot(x) dx = -csc(x) + C $
\end{itemize}

\end{document}
